\section{Data}
\label{sec:data}
\subsection{HI and CO data}

Radio emission lines in $\atomHI$ and $\CO$ trace the two dominant constituents of the Galactic ISM, atomic and molecular gas. 
Ionized phases of the ISM do not contribute significantly to the column density and will therefore not trace the extinction measured in \citet{Green_2015}. 
21-cm line emission from the hyperfine transition of $\atomHI$ is usually optically thin and its integral is an excellent tracer of $\atomHI$ column:
\begin{equation}\label{XHI}
N_{HI} = 1.8 \times 10^{18} \rm cm^{-2} \frac{ \int T_B dv}{\rm K~km/s}.
\end{equation}
The 21-cm line can become optically thick, meaning equation \ref{XHI} underestimates the HI column, but this mostly happens in $\molH$ dominated regions \citep{Goldsmith_2007}. 

We trace molecular gas here using the 115 GHz 1-0 rotational transition of $\CO$. 
The integral of this emission line can be converted to a $\molH$ column density using the conversion factor \citep{Bolatto_2013}

\begin{equation}\label{XCO}
X_{CO} = 2.0 \times 10^{20} \rm cm^{-2} \frac{ \int T_B dv}{\rm K~km/s}.
\end{equation}

This conversion factor has number of known weaknesses, stemming from much more complex excitation and opacity effects, as well as real variation in relative population of $\CO$ and $\molH$ molecules. 
We will address the impacts of these weaknesses in \S \ref{sec:validation}. 

For our $\CO$ data, we use the interpolated whole Galaxy cube provided by \citet{Dame_2001}. 
We post-process these data with a plus-shaped median smoothing kernel to eliminate single-pixel artifacts in the data. 
This filtering procedure generates less than {\bf TK\%} effect in the total CO emission contained in the map. 
{\bf REVISE THIS} In this text, we investigate the Galactic plane and so use the sky area provided in this data set, $-30^\circ < b < 30^\circ$, and over the full range of $l$ as our grid. {\bf REVISE THIS}
These data have a radial velocity resolution of 1.3 km s$^{-1}$ and a velocity range of -320 km s$^{-1} < V_{LSR} <$ 320 km s$^{-1}$. 
We find that the native resolution and PPV extent of these data are appropriate for our investigation and retain the exact pixelization of these data for our analysis. 

For our $\atomHI$ data we use a combination of three large-area Galactic $\atomHI$ surveys. 
South of declination 0$^\circ$ we use data from the 16$^\prime$ resolution GASS survey \citep{Kalberla_2010}, from declination 0$^\circ$ to 38$^\circ$ we use unpublished data from the 4$^\prime$ resolution GALFA-HI survey \citep{Peek_2011} Data Release 2, North of 38$^\circ$ we default to the 36$^\prime$ resolution LAB Survey \citep{Kalberla_2005}. 
We regrid these data onto the $7.5^\prime \times 1.3$km s$^(-1}$ pixels of the \citet{Dame_2001} $\CO$ map.
These two maps are then combined using the above equations \ref{XHI} and \ref{XCO} to make a single $\mathrm{N_H}$ data cube.


\subsection{Dust data}

Our extinction cube is derived entirely from the \citet{Green_2015} reddening data. 
\citet{Green_2015} use PanSTARRS photometry of 800 million stars to infer the cumulative reddening along the line of sight in 6.8$^\prime$ (NSIDE=512 HEALPix) pixels. 
The distance information provided by the \citet{Green_2015} map is in steps of half a distance modulus, from 63 pc to 63 kpc. 
We regrid these data onto the \citet{Dame_2001} $\glon-\glat$ grid and difference them in distance to find the reddening between each distance modulus. 
This differential reddening is then converted to a hydrogen column using the factor measured in \citet{Peek_2013}, 

\begin{equation}
\mathrm{N_H} = E\left(B-V\right) 7 \times 10^{21} \frac{\rm cm^{-2} }{\rm mag}. 
\end{equation}


\subsection{High-mass star forming region data}
\label{sec:data-HMSFR}
To check the accuracy of our method, we need measurements of the line-of-sight velocities and distances of clouds of gas. 
\Reid{} have measured the line-of-sight velocities, proper motions, and trigonometric parallaxes of water and methanol masers associated with 103 high-mass star forming regions (HMSFRs). 
Of these 103, 99 fall inside the region of the Milky Way we consider in our solution.
We adopt the line-of-sight velocities, velocity uncertainties, and parallaxes of these 99 HMSFRs as stated in Table 1 of \Reid{}. 
Following the discussion in CITET BOVY, we assume that the parallax uncertainties correspond to distance uncertainties of approximately 10\%. 
