\subsection{Catastrophic outliers}
\label{sec:discussion-catastrophic}
In this section, we discuss the five HMSFRs where the KT-derived and directly observed $\vlos$ values are clearly inconsistent.
The distribution of standardized residuals of the HMSFR sample is shown in panel (a) of Figure \ref{fig:outliers}; the five outlier HMSFRs are marked in red.
The reason why these five HMSFRs, specifically, are outliers seems to be that they are located in a particularly complex and confused part of the Galaxy.
From panels (b), (c), and (d) of the same Figure, one can see that all of the outliers are in the inner Galaxy and relatively close to the Galactic center, at $0^\circ < \glon < 35^\circ$ and $\RGC < 6\text{ kpc}$. 
If we compare the distributions of all HMSFRs and outlier HMSFRs in $\glon$ and $\RGC$, it should be apparent that the distribution of outliers does not follow the distribution of all HMSFRs.

We can quantify this deviation by assuming that any HMSFR is equally likely to be one of the five outliers and computing the probability of finding all five in a randomly chosen subsample of the same size as one of our two selections.
Since a single HMSFR can not be present in a sample twice, the appropriate distribution to use for this calculation is the hypergeometric distribution, which assumes that the subsample is chosen without replacement.
The probability of finding all five outliers in a random subsample the size of either of the two selections is, in both cases, much less than 1\%.

The implication of this difference in distribution is that there is an actual enhancement in the rate at which KT produces incorrect solutions for sightlines that pass near the Galactic center. 
There are three main reasons why KT would be less accurate along a sightline at low $\glon$.
Firstly, these sightlines pass through more matter, due to both the increase in ISM surface density at low $\RGC$ and the fact that geometrically, a sightline at low $\glon$ will pass through more of the far side of the Galaxy.
Having more matter along a sightline increases the complexity of the problem --- more parcels of ISM in PPD space have to be correctly associated with velocity components in PPV space.
Secondly, due in part to the increase in ISM surface density with decreasing $\RGC$, the well-measured part of the PPD cube does not extend as far towards the inner Galaxy as it does towards the outer Galaxy \citep{Green_2015}. 
If the PPD cube is not accurate past some distance, then we are unlikely to obtain a correct solution past that distance.
Thirdly, the Galactic bar can stir interstellar matter up, inducing a complicated velocity field with lots of structure on small spatial scales. 
Given that the distance extent of PPD voxels near the inner Galaxy is of order a kpc, we could simply have insufficient spatial resolution to map this bar-induced velocity field. 

Two of these three reasons are caused by being at low $\glon$ while the other is caused by being in a specific $\RGC$ range. 
To try to differentiate between the two possible causes, we can repeat the quantitative exercise described above with the $\RGC$ selection as the subsample and the $\glon$ selection, rather than the full set of 99 HMSFRs, as the population. 
The probability of finding all five outliers in a random 21-element subsample of the 31-element $\glon$ selection is about 11\%. 
This probability is low but not unreasonable; we cannot differentiate between the two causes in this way.
